Presentation Title

### 2017-08-15 paper/s3-system.tex
Edit paper

To describe our system, we first give an informal overview and then move on to the formal description.
Unlike most blockchain systems, we do not use a global ledger.
Instead, every node has their own hash chain.
The nodes only store transactions (TX) that they are involved in on their hash chain.
Transactions are stored in TX blocks and every block only contains one transaction.
We introduce a special block called checkpoint (CP) block, which represents the state of a hash chain.
Such data structure is called Extended TrustChain,
a visualisation can be seen on~\Cref{fig:trustchain-good-cp}.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{trustchain-good-cp}
\caption{Visualisation of the Extended TrustChain. $t_{u, i}$ represents a TX block on $u$'s chain with a sequence number of $i$.
$c_{v, j}$ represents a CP block on $v$'s chain with a sequence number of $j$.}
\label{fig:trustchain-good-cp}
\end{figure}

We randomly elect $n$ special nodes called facilitators in every round.
The facilitators reach consensus on CP blocks using an existing consensus algorithm---asynchronous subset consensus from HoneyBadgerBFT~\cite{miller2016honey}.
The consensus result is essentially a set of CP blocks from (nearly) all the nodes.
While this gives us consensus on a representation of the global state, it does not imply consensus on transactions.
To this end, we introduce a validation protocol that allows any nodes to challenge any other node to produce a set of TX blocks that computes to the CP block in consensus.
Hence we implicitly achieve consensus on transactions.
Since the transaction and validation protocols only make point-to-point communication,
we achieve horizontal scalability.

The formal description is given next,
it consist of one data structure---Extended TrustChain,
and three protocols---consensus protocol, transaction protocol and validation protocol.

\subsection{Extended TrustChain}
Each node $u$ has a public and private key pair---$pk_u$ and $sk_u$, and a chain $B_u$.
The chain consist of blocks $B_u = \{ b_{u, i} : i \in \{ 0, \dots, h - 1 \} \}$,
where $b_{u, i}$ is the $i$th block of $u$,
and $h$ is the height of the block (i.e. $h = |B_u|$).
We often use $b_{u, h}$ to denote the latest block.
There are two types of blocks, TX blocks and CP blocks.
If $T_u$ is the set of all TX blocks in $B_u$ and $C_u$ is the set of all CP blocks is $B_u$,
then it must be the case that $T_u \cup C_u = B_u$ and $T_u \cap C_u = \varnothing$.
The notation $b_{u, i}$ is generic over the block type.
We assume there exists a function $\textsf{typeof}: B_u \rightarrow \{ \tau, \gamma \}$ that returns the type of the block,
where $\tau$ represents the TX type and $\gamma$ represents the CP type.

@@

The TX block is a six-tuple, i.e
$$t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle.$$
We describe each item in turn.
\begin{enumerate}
\item $\textsf{H}(b_{u, i - 1})$ is the hash pointer to the previous block.
\item $seq_u$ is the sequence number which should equal $i$.
\item $txid$ is the transaction identifier, it should be generated using a cryptographically secure pseudo-random number generator by the initiator of the transaction.
\item $pk_v$ is the public key of the counterparty $v$.
\item $m$ is the transaction message.
\item $sig_u$ is the signature created using $sk_u$ on the concatenation of the binary representation of the five items above.
\end{enumerate}
The fact that we have no constraint on the content of $m$ is in alignment with our problem description---application neutrality.

TX blocks come in pairs.
In particular, for every block 
$$t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle$$
there exist one and only one \emph{pair} 
$$t_{v, j} = \langle \textsf{H}(b_{v, j - 1}), seq_v, txid, pk_u, m, sig_v \rangle.$$
Note that the $txid$ and $m$ are the same, and the public keys refer to each other.
Thus, given a TX block, these properties allow us to identify its pair.
\end{definition}

@@

Here we define an important property which results from the interleaving nature of CP and TX blocks.
It is used in our validation protocol.
\begin{definition}
\textbf{\emph{Enclosure and agreed enclosure}}

If there exist a tuple $\langle c_{u,a}, c_{u, b} \rangle$ for a TX block $t_{u, i}$,
where 
$$a = \argmin_{k, k < i, \texttt{typeof}(b_{u,k}) = \gamma}(i - k)$$
$$b = \argmin_{k, k > i, \texttt{typeof}(b_{u,k}) = \gamma}(k - i),$$
then $\langle c_{u,a}, c_{u, b} \rangle$ is the enclosure of $t_{u, i}$.
Intuitively, that is the two closest CP blocks that surround $t_{u, i}$.
Note that $c_{u, a}$ is the more recent CP block.
Also, some TX blocks may not have any enclosure, then its enclosure is $\bot$.
Agreed enclosure is the same as enclosure with an extra constraint where the CP blocks must be in some consensus result $\C_r$.
\end{definition}

@@

\subsection{Consensus Protocol}
Our scalable consensus protocol runs on top of Extended TrustChain.
It uses an unmodified asynchronous subset consensus (ACS) algorithm as the key building block (we describe the reasoning later).
The objectives of the protocol are to
allow honest nodes always make progress (in the form of creating new CP blocks),
compute correct consensus result in every round
and have an unbiased election of facilitators.
Concretely, we define the necessary properties as follows.
\begin{definition}
\label{def:consensus}
\textbf{\emph{Properties of the consensus protocol}}

@@

\subsubsection{Bootstrap phase}
\label{sec:bootstrap}
As with many distributed systems, there must be a bootstrap phase which sets up the system.
Imagine that there is some bootstrap oracle, that initiates the code on every node.
The code satisfies all the properties in \Cref{def:consensus}.
Namely, every node has the same set of valid facilitators $\F_1$ that are randomly chosen.
This concludes the bootstrap phase.
For any future rounds, the consensus phase is used.

\subsubsection{Consensus phase}
\label{sec:consensus-phase}
The consensus phase begins when $\F_r$ is available to all the nodes.
Note that $\F_r$ indicates the facilitators that were elected using results of round $r$ and are responsible for driving the ACS protocol in round $r + 1$.
The goal is to reach agreement on a set of new facilitators $\F_{r + 1}$ that satisfies the four properties in \Cref{def:consensus}.

@@

Upon receiving $\C_{r + 1}$ and at least $n - f$ valid signatures by some node $u$, $u$ performs two tasks.
First, it creates a new CP block using $\textsf{new\_cp}(\C_{r + 1}, r + 1)$ using \Cref{alg:new-cp}.
Second, it computes the new facilitators using $\textsf{get\_facilitator}(\C_{r + 1}, n)$ (\Cref{alg:facilitator}),
and updates its facilitator set to the result.
This concludes the consensus phase and brings us back to the state at the beginning of the consensus phase,
so a new round can be started.

\begin{algorithm}
\caption{Function $\textsf{new\_cp}(\C_r, r)$ runs in the context of the caller $u$.
It creates a new CP block and appends it to $u$'s chain.}
\label{alg:new-cp}
\begin{algorithmic}
\State $h \gets |B_u|$
\State $c_{u, h} \gets \langle \textsf{H}(b_{u, h-1}), h, \textsf{H}(\C_r), r, sig_u \rangle$
\State $B_u \gets B_u \cup c_{u, h}$
\end{algorithmic}
\end{algorithm}

@@

\subsection{Validation protocol}
\label{sec:vd-protocol}

Up to this point, we do not provide a mechanism to detect tampering.
The validation protocol aims to solve this issue.
The protocol is also a request-response protocol, just like the transaction protocol.
But before explaining the protocol itself, we first define what it means for a transaction to be valid.

\subsubsection{Validity definition}
A transaction can be in one of three states in terms of validity---\emph{valid}, \emph{invalid} and \emph{unknown}.
Given a fragment $F_{v, j}$,
the validity of the TX block $t_{u, i}$ with its corresponding fragment $F_{u, i}$ is captured by the function $\textsf{get\_validity}(t_{u, i}, F_{u, i}, F_{v, j})$ (\Cref{alg:get-validity}).
Note that $t_{u, i}$ and $F_{u, i}$ are assumed to be valid,
otherwise the node calling the function would have no point of reference.
This is not difficult to achieve,
because typically the caller is $u$, so it knows its own TX block and the corresponding agreed fragment.
If the caller is not $u$, it can always query for the agreed fragment that contains the transaction of interest from $u$.

@@

Note that the validity is on a transaction (two TX blocks with the same $txid$), rather than on one TX block owned by a single party.
It is defined this way because the malicious sender may create new TX blocks in their own chain but never send \texttt{tx\_req} messages.
In that case, it may seem that the counterparty, who is honest, purposefully omitted TX blocks.
But in reality, it was the malicious sender who did not follow the protocol.
Thus, in such cases, the whole transaction identified by its $txid$ is marked as invalid.

@@

\subsubsection{Validation protocol}
Our validation protocol,
shown in~\Cref{alg:vd-proto},
is designed to classify transactions according to the aforementioned validity definition.
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties of the validation protocol are as follows.
\begin{definition}
\label{def:validation}
\textbf{\emph{Properties of the validation protocol}}

@@

We make two remarks.
First, just like the TX protocol, we do not block at any part of the protocol.
Second, suppose some $F_{v, j}$ validates $t_{u, i}$, then that does not imply that $t_{u, i}$ only has one pair $t_{v, j}$.
Our validity requirement only requires that there is only one $t_{v, j}$ in the correct consensus round.
The counterparty may create any number of fake pairs in later consensus rounds.
But these fake pairs only pollutes the chain of $v$ and can never be validated because the round is incorrect.

\subsection{Design variations and tradeoffs}
\label{sec:tradeoffs}
In this section, 
we explore a few design variations which we can make, some of them require a relaxed version of our original model.
They enable better performance and allow us to apply our design in the fully permissionless setting.

\subsubsection{Using timing assumption in the permissionless setting}
\label{sec:permissionless}
One limitation of our system is that we use the parameter $N$ in our algorithms, which makes it unsuitable for the permissionless environment where users can join and leave at will.
In this section we show how making a timing assumption would allow us to operate in the permissionless setting.

At the start of our consensus phase (\Cref{sec:consensus-phase}), facilitators must wait for $N-f$ \texttt{cp\_msg} messages.
This is the only place where we used $N$ as a parameter.
To introduce timing, instead of waiting for $N-f$ messages, we wait for some time $D$,
such that $D$ is sufficiently long for honest nodes to send their CP blocks to the facilitators.
Consequently, this removes the need for a PKI because the collected CP blocks may be from nodes that nobody has seen in the past.

@@

\subsubsection{Optimising validation protocol using cached agreed fragments}
\label{sec:caching}
One more way to improve the efficiency of the validation protocol is to use a single agreed fragment to validate multiple transactions.
Concretely, for node $A$, upon receiving an agreed fragment from node $B$,
rather than validating a single transaction,
$A$ attempts to validate all transactions with performed with $B$ in the unknown state, in that fragment.

@@

\subsubsection{Total fork detection}
\label{sec:fork}
The validation algorithm guarantees that there are no forks within a single agreed fragment.
This is sufficient for some applications such as proving the existence of some information.
However, for applications such as digital cash where every block depends on one or more previous blocks,
our scheme is not suitable.
For such applications, we need to guarantee that there are no forks from the genesis block leading up to the TX block of interest.

@@

The second approach is probabilistic but with only a constant communication overhead over our current design.
For a node, observe that if all of its agreed fragments has a transaction with an honest node,
then the complete chain is effectively validated in a distributed manner.
The only way for an attacker to make a fork is to make sure that the agreed fragment containing the fork has no transactions with honest nodes.
Such malicious behaviour is prevented probabilistically using a challenge-response protocol as follows.
Suppose node $A$ wish to make a transaction with node $B$.
$A$ first sends a challenge to $B$ asking it to prove that it holds a valid agreed fragment between some consensus round specified by $A$.
If $B$ provides a correct proof, then they run the transaction protocol as usual.
If $B$ provides an invalid proof or refuses to respond,
then $A$ would refuse to make the transaction.

>>>>

To describe our system, we first give an informal overview and then move on to the formal description.
Unlike most blockchain systems, we do not use a global ledger.
Instead, every node has their own hash chain.
The nodes only store transactions (TX) that they are involved in on their hash chain.
Transactions are stored in TX blocks and every block only contains one transaction.
We introduce a special block called checkpoint (CP) block,
which represents the state of a hash chain in the form of a hash pointer.
Such data structure is called Extended TrustChain,
a visualisation can be seen in~\Cref{fig:trustchain-good-cp}.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{trustchain-good-cp}
\caption{Visualisation of the Extended TrustChain. $t_{u, i}$ represents a TX block on $u$'s chain with a sequence number of $i$.
$c_{v, j}$ represents a CP block on $v$'s chain with a sequence number of $j$.
A transaction is represented by a \emph{pair} of TX blocks,
one on each of the party's chain.
}
\label{fig:trustchain-good-cp}
\end{figure}

We randomly elect $n$ special nodes called facilitators in every round.
The facilitators reach consensus on CP blocks using an existing consensus algorithm---asynchronous subset consensus from HoneyBadgerBFT~\cite{miller2016honey}.
The consensus result is essentially a set of CP blocks from (nearly) all the nodes.
While this gives us a consensus on a representation of the global state, it does not imply consensus on transactions.
To this end,
we introduce a validation protocol that allows any nodes to challenge any other node to produce a set of TX blocks that computes to the CP block in consensus,
achieving implicit consensus on transactions.
Since the transaction and validation protocols only make point-to-point communication,
we achieve horizontal scalability.

The formal description is given next,
it consists of one data structure---Extended TrustChain,
and three protocols---consensus protocol, transaction protocol and validation protocol.
The complete protocol can be seen as the concurrent composition of the sub-protocols.

\subsection{Extended TrustChain}
Each node $u$ has a public and private key pair---$pk_u$ and $sk_u$, and a chain $B_u$.
The chain consists of blocks $B_u = \{ b_{u, i} : i \in \{ 0, \dots, h - 1 \} \}$,
where $b_{u, i}$ is the $i$th block of $u$,
and $h$ is the height of the block (i.e. $h = |B_u|$).
We often use $b_{u, h}$ to denote the latest block.
There are two types of blocks, TX blocks and CP blocks.
If $T_u$ is the set of all TX blocks in $B_u$ and $C_u$ is the set of all CP blocks is $B_u$,
then it must be the case that $T_u \cup C_u = B_u$ and $T_u \cap C_u = \varnothing$.
The notation $b_{u, i}$ is generic over the block type.
We assume there exists a function $\textsf{typeof}: B_u \rightarrow \{ \tau, \gamma \}$ that returns the type of the block,
where $\tau$ represents the TX type and $\gamma$ represents the CP type.

@@

The TX block is a six-tuple, i.e
$$t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle.$$
We describe each item in turn.
\begin{enumerate}
\item $\textsf{H}(b_{u, i - 1})$ is the hash pointer to the previous block.
\item $seq_u$ is the sequence number which should equal $i$.
\item $txid$ is the transaction identifier, it should be generated using a cryptographically secure pseudo-random number generator by the initiator of the transaction.
\item $pk_v$ is the public key of the counterparty $v$.
\item $m$ is the transaction message,
    which can be seen as an arbitrary string.
\item $sig_u$ is the signature created using $sk_u$ on the concatenation of the binary representation of the five items above.
\end{enumerate}
% The fact that we have no constraint on the content of $m$ is in alignment with our problem description---application neutrality.

TX blocks come in pairs.
In particular, for every block 
$$t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle$$
there exist one and only one \emph{pair} 
$$t_{v, j} = \langle \textsf{H}(b_{v, j - 1}), seq_v, txid, pk_u, m, sig_v \rangle,$$
if the nodes follow the transaction protocol (described in~\Cref{sec:tx-protocol}).
Note that the $txid$ and $m$ are the same, and the public keys refer to each other.
Thus, given a TX block, these properties allow us to identify its pair.
\end{definition}

@@

Here we define an important property which results from the interleaving nature of CP and TX blocks.
It is used in our validation protocol (discussed in~\Cref{sec:vd-protocol}).
\begin{definition}
\textbf{\emph{Enclosure and agreed enclosure}}

If there exist a tuple $\langle c_{u,a}, c_{u, b} \rangle$ for a TX block $t_{u, i}$,
where 
$$a = \argmin_{k, k < i, \textsf{typeof}(b_{u,k}) = \gamma}(i - k)$$
$$b = \argmin_{k, k > i, \textsf{typeof}(b_{u,k}) = \gamma}(k - i),$$
then $\langle c_{u,a}, c_{u, b} \rangle$ is the enclosure of $t_{u, i}$.
Intuitively, that is the two closest CP blocks that surround $t_{u, i}$.
Some TX blocks may not have any enclosure, then its enclosure is $\bot$.
Agreed enclosure is the same as enclosure with an extra constraint where the CP blocks must be in some consensus result $\C_r$.
\end{definition}

@@

\subsection{Consensus Protocol}
Our scalable consensus protocol runs on top of Extended TrustChain.
It uses an unmodified asynchronous subset consensus (ACS) algorithm as the key building block.
The objectives of the protocol are to
allow honest nodes always make progress (in the form of creating new CP blocks),
compute correct consensus result in every round
and have an unbiased election of facilitators.
Concretely, we define the necessary properties as follows.
\begin{definition}
\label{def:consensus}
\textbf{\emph{Properties of the consensus protocol}}

@@

\subsubsection{Bootstrap Phase}
\label{sec:bootstrap}
As with many distributed systems, there must be a bootstrap phase which sets up the system.
Imagine that there is some bootstrap oracle, that initiates the code on every node.
The code satisfies all the properties in \Cref{def:consensus}.
Namely, every node has the same set of valid facilitators $\F_1$ that are randomly chosen.
This concludes the bootstrap phase.
For any future rounds, the consensus phase is used.

\subsubsection{Consensus Phase}
\label{sec:consensus-phase}
The consensus phase begins when $\F_r$ is available to all the nodes.
Note that $\F_r$ indicates the facilitators that were elected using results of round $r$ and are responsible for driving the ACS algorithm in round $r + 1$.
The goal is to reach agreement on a set of new facilitators $\F_{r + 1}$ that satisfies the four properties in \Cref{def:consensus}.

@@

Upon receiving $\C_{r + 1}$ and at least $n - f$ valid signatures by some node $u$, $u$ performs two tasks.
First, it creates a new CP block using $\textsf{new\_cp}(\C_{r + 1})$ (\Cref{alg:new-cp}).
Second, it computes the new facilitators using $\textsf{get\_facilitator}(\C_{r + 1}, n)$ (\Cref{alg:facilitator}),
and updates its facilitator set to the result.
This concludes the consensus phase and brings us back to the state at the beginning of the consensus phase,
so a new round can be started.

\begin{algorithm}
\caption{Function $\textsf{new\_cp}(\C_r)$ runs in the context of the caller $u$.
It creates a new CP block and appends it to $u$'s chain.}
\label{alg:new-cp}
\begin{algorithmic}
\State $\langle r, \_ \rangle \gets \C_r$
\State $h \gets |B_u|$
\State $c_{u, h} \gets \langle \textsf{H}(b_{u, h-1}), h, \textsf{H}(\C_r), r, sig_u \rangle$
\State $B_u \gets B_u \cup c_{u, h}$
\end{algorithmic}
\end{algorithm}

@@

\subsection{Validation Protocol}
\label{sec:vd-protocol}

Up to this point, we do not provide a mechanism to detect tampering.
The validation protocol aims to solve this issue.
The protocol is also a request-response protocol.
But before explaining the protocol itself, we first define what it means for a transaction to be valid.

\subsubsection{Validity Definition}
A transaction can be in one of three states in terms of validity---\emph{valid}, \emph{invalid} and \emph{unknown}.
Given a fragment $F_{v, j}$,
the validity of the TX block $t_{u, i}$ with its corresponding fragment $F_{u, i}$ is captured by the function $\textsf{get\_validity}(t_{u, i}, F_{u, i}, F_{v, j})$ (\Cref{alg:get-validity}).
Note that $t_{u, i}$ and $F_{u, i}$ are assumed to be valid,
otherwise the node calling the function would have no point of reference.
This is not difficult to achieve because typically the caller is $u$,
so it knows its own TX block and the corresponding agreed fragment.
If the caller is not $u$, it can always query for the agreed fragment that contains the transaction of interest from $u$.

@@

Note that the validity is on a transaction, i.e. two TX blocks that form a pair.
It is defined this way because the malicious sender may create new TX blocks in their own chain but never send \texttt{tx\_req} messages.
In that case, it may seem that the counterparty, who is honest, purposefully omitted TX blocks.
But in reality, it was the malicious sender who did not follow the protocol.
Thus, in such cases, the whole transaction identified by its $txid$ is marked as invalid.

@@

\subsubsection{Validation Protocol}
Our validation protocol,
shown in~\Cref{alg:vd-proto},
is designed to classify transactions according to the aforementioned validity definition.
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties of the validation protocol are as follows.
\begin{definition}
\label{def:validation}
\textbf{\emph{Properties of the validation protocol}}

@@

We make two remarks.
First, just like the TX protocol, we do not block any part of the protocol.
Second, suppose some $F_{v, j}$ validates $t_{u, i}$, then that does not imply that $t_{u, i}$ only has one pair $t_{v, j}$.
Our validity requirement only requires that there is only one $t_{v, j}$ in the correct consensus round.
The counterparty may create any number of fake pairs in later consensus rounds.
But these fake pairs only pollutes the chain of $v$ and can never be validated.

\subsection{Design Variations and Tradeoffs}
\label{sec:tradeoffs}
In this section, 
we explore a few design variations, some of them require a relaxed version of our original model.
They enable better performance and allow us to apply our design in the fully permissionless setting.

\subsubsection{Using Timing Assumption in the Permissionless Setting}
\label{sec:permissionless}
At the start of our consensus phase (\Cref{sec:consensus-phase}), facilitators must wait for $N-f$ \texttt{cp\_msg} messages.
The use of $N$ makes our system unsuitable for the permissionless setting.
To introduce timing, instead of waiting for $N-f$ messages, we wait for some time $D$,
such that $D$ is sufficiently long for honest nodes to send their CP blocks to the facilitators.
Consequently, this removes the need for a PKI because the collected CP blocks may be from nodes that nobody has seen in the past.

@@

\subsubsection{Optimising Validation Protocol Using Cached Agreed Fragments}
\label{sec:caching}
One more way to improve the efficiency of the validation protocol is to use a single agreed fragment to validate multiple transactions.
Concretely, for node $A$, upon receiving an agreed fragment from node $B$,
rather than validating a single transaction,
$A$ attempts to validate all transactions performed with $B$ in the unknown state, in that fragment.

@@

\subsubsection{Total Fork Detection}
\label{sec:fork}
The validation algorithm guarantees that there are no forks within a single agreed fragment.
This is sufficient for some applications such as proving the existence of some information.
However, for applications such as digital cash where every block depends on one or more previous blocks,
our scheme is not suitable.
For such applications, we need to guarantee that there are no forks from the genesis block leading up to the TX block of interest.

@@

The second approach is probabilistic but with only a constant communication overhead over our current design.
For a node, observe that if all of its agreed fragments has a transaction with an honest node,
then the complete chain is effectively validated in a distributed manner.
The only way for an attacker to make a fork is to make sure that the agreed fragment containing the fork has no transactions with honest nodes.
Such malicious behaviour is prevented probabilistically using a challenge-response protocol as follows.
Suppose node $A$ wish to make a transaction with node $B$.
$A$ first sends a challenge to $B$ asking it to prove that it holds a valid agreed fragment between some consensus round specified by $A$.
If $B$ provides a correct and timely response, then they run the transaction protocol as usual.
Otherwise, $A$ would refuse to make the transaction.

### 2017-08-15 paper/s4-analysis.tex
Edit paper

\section{Correctness and fault tolerance analysis}
\label{sec:analysis}
We evaluate our system analytically to ensure the desired properties (\Cref{def:consensus} and \Cref{def:validation}) hold.
An informal argument is given in this section, we refer to~\cite[Chapter 4]{checo}??? for an in-depth analysis.

\subsection{Correctness of the consensus protocol}
Recall that the consensus protocol properties (\Cref{def:consensus}) has
four items---agreement, validity, termination and fairness.
The first three hold due to the following facts.
\begin{itemize}
    \item The CP blocks sent to the facilitators are eventually delivered and then ACS eventually starts.
    \item Agreement, validity and termination holds for ACS as they are the properties of ACS and are proven to hold in~\cite{miller2016honey}.
    \item The consensus result and signatures are eventually disseminated to all the nodes,
        so honest nodes must hold the same result as the honest facilitators.
\end{itemize}

Fairness holds if we model $\textsf{H}(\cdot)$ as a query to the random oracle.
Sorting nodes by the luck value $\textsf{H}(\C || pk)$ can be seen as a random permutation of a list of nodes.
Therefore every node has the same probability of becoming a facilitator.

\subsection{Correctness of the validation protocol}
\label{sec:correctness-of-validity}
Using the previous result,
we show that the agreement and validity properties (from~\Cref{def:validation}) hold for the validation protocol.

The validity property holds because we use $\textsf{get\_validity}(\cdot)$ in the validation protocol.
The agreement property holds because we model $\textsf{H}(\cdot)$ as a query to a random oracle.
Suppose two honest nodes decided on two different state, \emph{valid} and \emph{invalid} for the same transaction.
Due to the properties of the consensus protocol, the agreed enclosure for the transaction must be the same.
For that to happen, two agreed fragments must exist for the same transaction.
Recall that blocks form a hash chain.
So this cannot happen unless the adversary can compute the inverse of $\textsf{H}(\cdot)$ with high probability.

Liveness, unfortunately does not hold in our model.
A malicious node can ask honestly when running the transaction protocol,
but then never respond to any validation requests.
Therefore there are transactions that can never be validated.
Nevertheless, the malicious node will be at an economical loss if it is not responsive because honest nodes are less likely to make contact with nodes that do not respond to validation requests.

@@

\subsection{Fault tolerance}
Finally, we consider the effect when the number of adversaries is more than $t$.
This is useful because in practice it is difficult to guarantee that $t$ satisfies $n \ge 3t + 1$,
especially when $N$ is large.
Hence we are interested in the probability for this to happen under our facilitator election process.
The problem is modelled by a hypergeometric distribution,
where the random variable $X$ is the number of malicious nodes.
For our system to fail, we are interested in the following probability.
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1]
$$
Let $E[X] = n\alpha$ where $0 \le \alpha \le \lfloor \frac{n-1}{3} \rfloor/n < (\lfloor  \frac{n - 1}{3} \rfloor + 1) / n$.
Using the tail inequality found in~\cite{skala2013hypergeometric}
$$
\Pr[X \ge E[X] + \tau n] \le e^{-2\tau^2n},
$$
and setting 
$$
\tau = \frac{\lfloor \frac{n-1}{3} \rfloor + 1}{n} - \alpha,
$$
we arrive at the following bound
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1] \le e^{-2 \big(\frac{\lfloor  \frac{n - 1}{3} \rfloor + 1}{n} - \alpha \big)^2 n}.
$$

The bound is not tight, but it is useful for picking parameters for a desired level of fault tolerance.
If $n$ is known, then we can pick a $\alpha$ such that the probability becomes small.
On the other hand, if $\alpha$ is fixed, but small, we may increase $n$ to achieve the same.
Furthermore, hypergeometric distributions have light tails with ``faster-than-exponential fall-off''~\cite{skala2013hypergeometric}.
So the probability for picking more than $\lfloor \frac{n-1}{3} \rfloor$ malicious nodes drops of exponentially as the expected value moves away from $\lfloor \frac{n-1}{3} \rfloor$.
To put this into perspective,
suppose $n = 1000$ and $\alpha = 1/5$, i.e. a fifth of the nodes are malicious.
Then the probability to elect more malicious nodes than the threshold is only $2.6 \times 10^{-16}$.

>>>>

\section{Correctness and Fault Tolerance Analysis}
\label{sec:analysis}
We evaluate our system analytically to ensure the desired properties (\Cref{def:consensus} and \Cref{def:validation}) hold.
An informal argument is given in this section, we refer to~\cite[Chapter 4]{checo}??? for an in-depth analysis.

\subsection{Correctness of the Consensus Protocol}
Recall that the consensus protocol properties (\Cref{def:consensus}) has
four items---agreement, validity, termination and fairness.
The first three hold due to the following facts.
\begin{itemize}
    \item The CP blocks sent to the facilitators are eventually delivered and then ACS eventually starts.
    \item Agreement, validity and termination hold for ACS as they are the properties of ACS and are proven to hold in~\cite{miller2016honey}.
    \item The consensus result and signatures are eventually disseminated to all the nodes,
        so honest nodes must hold the same result as the honest facilitators.
\end{itemize}

Fairness holds because we model $\textsf{H}(\cdot)$ as a query to the random oracle.
Sorting nodes by the luck value $\textsf{H}(\C || pk)$ can be seen as a random permutation of a list of nodes.
Therefore every node has the same probability of becoming a facilitator.

\subsection{Correctness of the Validation Protocol}
\label{sec:correctness-of-validity}
Using the previous result,
we show that the agreement and validity properties (from~\Cref{def:validation}) hold for the validation protocol.

The validity property holds because we use $\textsf{get\_validity}(\cdot)$ in the validation protocol.
The agreement property holds because we model $\textsf{H}(\cdot)$ as a query to a random oracle.
Suppose two honest nodes decided on two different states, \emph{valid} and \emph{invalid} for the same transaction.
For that to happen, two agreed fragments must exist for the same transaction,
but these fragments must also have the same agreed enclosure.
Recall that blocks form a hash chain.
So this is not possible unless the adversary can compute the inverse of $\textsf{H}(\cdot)$ with high probability.

Liveness, unfortunately, does not hold in our model.
A malicious node can act honestly when running the transaction protocol,
but then never respond to any validation requests.
Therefore there are transactions that can never be validated.
Nevertheless, the malicious node will be at an economic loss if it is not responsive because honest nodes are less likely to make contact with nodes that do not respond to validation requests.

@@

\subsection{Fault Tolerance}
Finally, we consider the effect when the number of adversaries is more than $t$.
This is useful because in practice it is difficult to guarantee that $t$ satisfies $n \ge 3t + 1$,
especially when $N$ is large.
Hence we are interested in the probability for this to happen under our facilitator election process.
The problem is modelled by a hypergeometric distribution,
where the random variable $X$ is the number of malicious nodes.
For our system to fail, we are interested in the following probability.
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1]
$$
Let $E[X] = n\alpha$ where $0 \le \alpha \le \lfloor \frac{n-1}{3} \rfloor/n$.
Using the tail inequality found in~\cite{skala2013hypergeometric}
$$
\Pr[X \ge E[X] + \tau n] \le e^{-2\tau^2n},
$$
and setting 
$$
\tau = \frac{\lfloor \frac{n-1}{3} \rfloor + 1}{n} - \alpha,
$$
we arrive at the following bound
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1] \le e^{-2 \big(\frac{\lfloor  \frac{n - 1}{3} \rfloor + 1}{n} - \alpha \big)^2 n}.
$$

The bound is not tight, but it is useful for picking parameters for the desired level of fault tolerance.
If $n$ is known, then we can pick a $\alpha$ such that the probability becomes small.
On the other hand, if $\alpha$ is fixed, we may increase $n$ to achieve the same.
Furthermore, hypergeometric distributions have light tails with ``faster-than-exponential fall-off''~\cite{skala2013hypergeometric}.
So the probability of picking more than $\lfloor \frac{n-1}{3} \rfloor$ malicious nodes drops of exponentially as the expected value moves away from $\lfloor \frac{n-1}{3} \rfloor$.
To put this into perspective,
suppose $n = 1000$ and $\alpha = 1/5$, i.e. a fifth of the nodes are malicious.
Then the probability to elect more malicious nodes than the threshold is only $2.6 \times 10^{-16}$.

### 2017-08-15 paper/s5-evaluation.tex
Edit paper

The prototype implementation can be found on GitHub.
\begin{displayquote}
\url{https://github.com/kc1212/consensus-thesis-code}
\end{displayquote}
It implements the three protocols and the Extended TrustChain.
We also implement the caching optimisations discussed in \Cref{sec:caching}.
It is written in the Python programming language\footnote{\url{https://www.python.org/}}.
The cryptography primitives we use are SHA256 for hash functions and Ed25519 for digital signatures.
Both of which are provided by libnacl~\footnote{\url{https://pypi.python.org/pypi/libnacl}}.

@@

To coordinate nodes on many different machines,
we employ a discovery server to inform every node the IP addresses and port numbers of every other node.
It is only run before the experiment and is not used during the experiment.

The global throughput results are shown in~\Cref{fig:global-throughput-fixed} and \Cref{fig:global-throughput-random}.
We consider~\Cref{fig:global-throughput-fixed} as the ideal case,
where nodes only make transactions with a fixed node.
We consider \Cref{fig:global-throughput-random} as the worst case,
where nodes make transactions with random nodes and the caching mechanism is unlikely to be used.
The low transaction rate in~\Cref{fig:global-throughput-random} is caused by the fact that the network infrastructure cannot keep up with our demand.
In practice, we do not expect such behaviour to occur as it is possible to cache agreed fragments.

@@

Overall, the throughput has a linear relationship with the population size.
This result is a strong indication of the horizontal scalability which we aimed to achieve.
For more experimental results, refer to~\cite[Chapter 5]{checo}???.

>>>>

The prototype implementation can be found on GitHub.
\begin{displayquote}
\url{https://github.com/kc1212/checo}
\end{displayquote}
It implements the three protocols and the Extended TrustChain.
We also implement the caching optimisation discussed in \Cref{sec:caching}.
It is written in the Python programming language\footnote{\url{https://www.python.org/}}.
The cryptography primitives we use are SHA256 for hash functions and Ed25519 for digital signatures.
Both of which are provided by libnacl~\footnote{\url{https://pypi.python.org/pypi/libnacl}}.

@@

The global throughput results are shown in~\Cref{fig:global-throughput}.
We consider~\Cref{fig:global-throughput-fixed} as the ideal case,
where nodes only make transactions with a fixed node.
We consider \Cref{fig:global-throughput-random} as the worst case,
where nodes make transactions with random nodes and the caching mechanism is unlikely to be used.
Observe that the transaction rate is much lower in~\Cref{fig:global-throughput-random}.
This is because the communication of an agreed fragment is necessary to verify every transaction (no caching),
putting a strain on our network infrastructure.
In practice, we do not expect such behaviour to occur as it is possible to cache agreed fragments.

@@

Overall, the throughput has a linear relationship with the population size.
This result is a strong indication of the horizontal scalability which we aimed to achieve.
For more experimental results refer to~\cite[Chapter 5]{checo}???.
